### 2023-09-10 paper/chapter/closure.tex
Refactor

% Como se resuelve la no-terminacion
% La prueba tambien sirve para STLC

\section{Trabajo futuro}
\subsection{Inferencia de tipos}
\subsection{Formalizar SIP}