### 2023-09-10 paper/paper.tex

\documentclass[]{report}
\usepackage[a4paper]{geometry}
\usepackage[spanish]{babel}
\usepackage{hyperref}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{listings}
\usepackage{ebproof}
\usepackage{float}
\usepackage[conor]{agda}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage[style=alphabetic]{biblatex}
\addbibresource{references.bib}
\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing,calc,tikzmark,calligraphy}
\usetikzlibrary{arrows.meta,positioning,matrix}
\setlength{\headheight}{13.07225pt}

%opening
\title{Formalización de Sistema I con tipo Top}
\author{Agustin Settimo}

\begin{document}

	\maketitle
	\tableofcontents

	\begin{abstract}

	\end{abstract}

	\chapter{Introducción}
	\input{chapter/intro}

	\chapter{Preliminares}
	\input{chapter/prelim}

	\chapter{Aportes}
	\input{chapter/contribution}

	\chapter{Conclusiones}
	\input{chapter/closure}

	\printbibliography

\end{document}