### 2024-01-08 slides/chapter/strong-norm.tex
Add chapters

\begin{frame}{Definición}
	\begin{center}
		\begin{prooftree}
			\hypo{ \forall t. s \hookrightarrow t \implies t \in SN }
			\infer1{ s \in SN }
		\end{prooftree}
	\end{center}

	\pause

	\ExecuteMetaData[code/SN1.tex]{sn-def}

	%\ExecuteMetaData[code/SN3.tex]{adequacy-proof}
\end{frame}

\begin{frame}{Ejemplos}
	\ExecuteMetaData[code/example.tex]{sn}
\end{frame}

\begin{frame}{Approach 1}
	\begin{AgdaSuppressSpace}
		\ExecuteMetaData[code/SN1.tex]{strong-type}

		\pause

		\ExecuteMetaData[code/SN1.tex]{strong-proof}
	\end{AgdaSuppressSpace}
\end{frame}

\begin{frame}{Approach 1}
	\ExecuteMetaData[code/SN1.tex]{lemma-abs}
\end{frame}

\begin{frame}{Approach 1}
	\ExecuteMetaData[code/SN1.tex]{lemma-app}
\end{frame}

\begin{frame}{Approach 2}
	\ExecuteMetaData[code/SN2.tex]{sn-star}
	\pause
	\ExecuteMetaData[code/SN2.tex]{sn-star-sn}
	\pause
	\ExecuteMetaData[code/SN2.tex]{inter}
\end{frame}

\begin{frame}{Approach 2}
	\ExecuteMetaData[code/SN2.tex]{adequacy-type}

	\ExecuteMetaData[code/SN2.tex]{strong-proof}

	\ExecuteMetaData[code/SN2.tex]{lemma-app}
	\ExecuteMetaData[code/SN2.tex]{adequacy-proof}
\end{frame}

\begin{frame}{Approach 3}
	\ExecuteMetaData[code/SN3.tex]{adequacy-type}

	\ExecuteMetaData[code/SN3.tex]{strong-proof}
\end{frame}

\begin{frame}{Approach 3}
	\ExecuteMetaData[code/SN3.tex]{subst-split}
	\ExecuteMetaData[code/SN3.tex]{adequacy-proof}
\end{frame}

\begin{frame}{Approach 4}
	\ExecuteMetaData[code/SN4.tex]{adequacy-subst}
	\pause
	\ExecuteMetaData[code/SN4.tex]{adequacy-ids}
	\pause
	\ExecuteMetaData[code/SN4.tex]{adequacy-cons}
	\pause
	\ExecuteMetaData[code/SN4.tex]{adequacy-type}
\end{frame}

\begin{frame}{Approach 4}
	\ExecuteMetaData[code/SN4.tex]{adequacy-proof}
	\ExecuteMetaData[code/SN4.tex]{strong-proof}
\end{frame}

\begin{frame}{Approach 4}
	\ExecuteMetaData[code/SN4.tex]{adequacy-exts}
	\ExecuteMetaData[code/SN4.tex]{sn-rename}
	\ExecuteMetaData[code/SN4.tex]{inter-rename}
\end{frame}

\begin{frame}{Approach 5}
	\ExecuteMetaData[code/SN5.tex]{inter}
	\ExecuteMetaData[code/SN5.tex]{inter-rename}
	\ExecuteMetaData[code/SN5.tex]{adequacy-rename}
\end{frame}

\begin{frame}{Approach 5}
	\ExecuteMetaData[code/SN5.tex]{subst-split}
	\ExecuteMetaData[code/SN5.tex]{adequacy-proof}
\end{frame}

\begin{frame}{Prueba para Sistema I}
	\ExecuteMetaData[code/strong_norm.tex]{SN}
	\ExecuteMetaData[code/strong_norm.tex]{sn-star}
\end{frame}

\begin{frame}{Prueba para Sistema I}
	\ExecuteMetaData[code/strong_norm.tex]{lemma-iso-type}
\end{frame}

\begin{frame}{Caso \textsc{comm}}
	\ExecuteMetaData[code/strong_norm.tex]{iso-comm}
\end{frame}

\section{Evaluación}